### 2018-08-22 TeX/organigram1.tex
a lot of changes

\documentclass[tikz, border={1000 750}]{standalone}
%%%% packages
\usepackage{tikz}
\usetikzlibrary{trees, arrows, shapes.geometric} % TikZ libraries
%%%% layers
\pgfdeclarelayer{bg1}    % declare background layer
\pgfdeclarelayer{bg2}
\pgfsetlayers{bg2,bg1,main}  % set the order of the layers (main is the standard layer)

%%%% styles
\tikzset{
  every rectangle node/.style = {draw=black,thick,anchor=west},
  io/.style = {rectangle, minimum width = 4cm, minimum height = 3cm, text centered, draw = black, fill = blue!10},
  main/.style = {rectangle, rounded corners, minimum width = 3cm, text centered, fill = purple!30},
  ids/.style = {diamond, minimum width = 3cm, minimum height = 2cm, text centered, draw = black, fill = green!30},
  res/.style = {rectangle, rounded corners, minimum width = 2cm, minimum height = 1cm, text centered, draw = black, fill = blue!30},
  resvariables/.style = {rectangle, minimum width = 2cm, minimum height = 1cm, text centered, draw = black},
  steps/.style = {rectangle, minimum width = 1cm, text centered, fill = yellow},
  arrow/.style = {->, > = stealth, draw = black, color = yellow!80, line width = 6pt}
}

\begin{document}
	\begin{tikzpicture}[auto,
	grow via three points={one child at (0.5,-1) and
		two children at (0.5,-1) and (0.5,-1.7)},
	edge from parent path={(\tikzparentnode.south) |- (\tikzchildnode.west)},
	remember picture, overlay, % r.p. save picture size in the picture, o. puts picture out of text segm.
	inner sep = 0pt, outer sep = 0pt
	]

		\node[text=red] (io) [io, align = left] at (0cm,0cm) {Table of Chemicals \\ CAS, Compound name};
		%% chemicals
		% id nodes

@@

		% main nodes
		\node (chemprop) [main, dashed, right of=cas, xshift=4.5cm, yshift=3cm] {CHEMPROP};
		\node (epa) [main, right of=cas, yshift=1cm, xshift=4.5cm] {EPA ectox tests}
			child { node { qu\_epa.R} };
		\node (chemscr) [main, right of=cas, yshift=-1cm, xshift=4.5cm] {Chemical scripts ch}
			child { node { Alan Wood Pesticide Compendium - \textbf{qu\_aw.R } }}
			child { node { Pesticide Action Network - \textbf{ch\_pan.R} }}
			child { node { PhysProp - \textbf{ch\_pp.R} }}
			child { node { PubChem - \textbf{qu\_pubchem.R} }};
		% result nodes
		\node (toxres) [resvariables, right of=cas, yshift=0cm, xshift=18cm, align = left] {Results\\Test results\\Substance type:\\pesticides, metals, etc.}; % result
		%\includegraphics{/home/andreas/Documents/Projects/etox-base/data/pubchemlogo2017.png};

@@

		%% organisms
		% id nodes
		\node (taxon) [ids, below of=cas, yshift=-9cm, align = center] {Taxon}; % \\ {(Genus or Species)}}; % escape brackets usin curly brackets
		% main nodes
		\node (taxonquery) [main, right of=taxon, xshift = 4.5cm, yshift = 3cm] {Taxonomic data};
		\node (habitat) [main, right of=taxon, xshift = 4.5cm, yshift = 1cm] {Habitat data}
			child { node { WORMS data base - \textbf{tx\_worms.R} }}
			child { node { Manual Search - \textbf{ha\_manual.R} }};
		\node (region) [main, right of = taxon, xshift = 4.5cm, yshift = -2cm] {Regional data}
			child { node { GBIF - \textbf{qu\_gbif.R} }};
		% result nodes
		\node (taxres) [resvariables, right of=taxon, xshift = 17cm, align = left] {Results:\\Validation of taxonomic ranks\\Habitat information\\Marine, Bracksih, Freshwater, Terrestrial, Parasites\\Occurrence}; % result

		%% final result
		\node (testres) [res, right of = cas, xshift = 22cm, yshift = -5cm] {Final result}
			child { node { re\_merge.R} };

@@

@@

		\draw [arrow, right of = testres] (testres) -- (20cm,-2cm);

>>>>

\documentclass[border = 1.5cm]{standalone}
%%%% packages
\usepackage{tikz}
\usetikzlibrary{trees, arrows, shapes.geometric, positioning} % TikZ libraries
%%%% layers
\pgfdeclarelayer{bg1}    % declare background layer
\pgfdeclarelayer{bg2}
\pgfsetlayers{bg2,bg1,main}  % set the order of the layers (main is the standard layer)

%%%% styles
\tikzset{
	every rectangle node/.style = {thick,anchor=west},
	io/.style = {rectangle, minimum width = 4cm, minimum height = 3cm, text centered, draw = black, fill = blue!10},
	main/.style = {rectangle, draw = black, rounded corners, minimum width = 3cm, minimum height = 1.25cm, text centered},
	ids/.style = {diamond, minimum width = 3cm, minimum height = 2cm, text centered, draw = black, fill = green!30},
	res/.style = {rectangle, rounded corners, minimum width = 2cm, minimum height = 1cm, text centered, draw = black, fill = blue!30},
	resvariables/.style = {rectangle, minimum width = 2cm, minimum height = 1cm, text centered},
	steps/.style = {rectangle, minimum width = 1cm, text centered, fill = yellow},
	arrow/.style = {->, > = stealth, draw = black, color = gray!80, line width = 3pt}
}

\begin{document}
	\begin{tikzpicture}[
	grow via three points={one child at (0.5,-1) and
		two children at (0.5,-1) and (0.5,-1.7)},
	edge from parent path={(\tikzparentnode.south) |- (\tikzchildnode.west)},
	inner sep = 0pt, outer sep = 0pt
	]

		\node (io) [io, align = left] at (0cm,0cm) {Table of Chemicals \\ CAS, Compound name};
		%% chemicals
		% id nodes

@@

		% main nodes
		\node (chemprop) [main, dashed, right of=cas, xshift=4.5cm, yshift=3cm] {CHEMPROP};
		\node (epa) [main, right of=cas, yshift=1cm, xshift=4.5cm] {EPA ectox tests}
			child { node { qu\_epa.R} };
		\node (chemscr) [main, right of=cas, yshift=-1cm, xshift=4.5cm] {Chemical scripts}
			child { node { Alan Wood Pesticide Compendium - \textbf{qu\_aw.R } }}
			child { node { Pesticide Action Network - \textbf{ch\_pan.R} }}
			child { node { PhysProp - \textbf{ch\_pp.R} }}
			child { node { PubChem - \textbf{qu\_pubchem.R} }};
		% result nodes
		\node (toxres) [resvariables, right of=cas, yshift=0cm, xshift=16cm, align = left] {Results\\Test results\\Substance type:\\pesticides, metals, etc.}; % result
		%\includegraphics{/home/andreas/Documents/Projects/etox-base/data/pubchemlogo2017.png};

@@

		%% organisms
		% id nodes
		\node (taxon) [ids, below of=cas, yshift=-9cm, align = center] {Taxon}; % \\ {(Genus or Species)}}; % escape brackets usin curly brackets
		% main nodes
		\node (taxonquery) [main, right of=taxon, xshift = 4.5cm, yshift = 3cm] {Taxonomic data};
		\node (habitat) [main, right of=taxon, xshift = 4.5cm, yshift = 1cm] {Habitat data}
			child { node { WORMS data base - \textbf{tx\_worms.R} }}
			child { node { Manual Search - \textbf{ha\_manual.R} }};
		\node (region) [main, right of = taxon, xshift = 4.5cm, yshift = -2cm] {Regional data}
			child { node { GBIF - \textbf{qu\_gbif.R} }};
		% result nodes
		\node (taxres) [resvariables, right of=taxon, xshift = 14cm, align = left] {Results:\\Validation of taxonomic ranks\\Habitat information\\Marine, Bracksih, Freshwater, Terrestrial, Parasites\\Occurrence}; % result

		%% final result
		\node (testres) [res, right of = cas, xshift = 18cm, yshift = -5cm] {Result}
			child { node { re\_merge.R} };
		\node (filtres) [res, right of = testres, xshift = 2cm] {Filter};
		\node (aggres) [res, right of = filtres, xshift = 2cm] {Aggregate};

@@

%		\draw [arrow] (epa.east) -| (testres.north);
%		\draw [arrow] (chemscr.east) -| (testres.north);

@@

		\draw [arrow, right of = testres] (testres) -- ++(2cm,0cm);

### 2018-08-22 TeX/organigram2.tex
a lot of changes

\documentclass{article}
%\usepackage{graphicx} % includegraphics
%% packages
\usepackage{tikz}
\usetikzlibrary{trees, arrows, shapes.geometric} % TikZ libraries
%\usetikzlibrary{backgrounds}
\usepackage{lscape}

%% layers
\pgfdeclarelayer{bg1}    % declare background layer
\pgfdeclarelayer{bg2}
\pgfsetlayers{bg2,bg1,main}  % set the order of the layers (main is the standard layer)

@@

\thispagestyle{empty} % removes the 1

% tree styles (defined by template)
\tikzstyle{every node}=[draw=black,thick,anchor=west]
%\tikzstyle{selected}=[draw=red,fill=red!30]
%\tikzstyle{optional}=[dashed,fill=gray!50]
% self defined
\tikzstyle{io}=[rectangle, minimum width = 4cm, minimum height = 1cm, text centered, draw = black, fill = blue!10]
\tikzstyle{main}=[rectangle, rounded corners, minimum width = 3cm, minimum height = 1cm, text centered, draw = black, fill = purple!30]
\tikzstyle{ids}=[diamond, minimum width = 3cm, minimum height = 1cm, text centered, draw = black, fill = green!30]
\tikzstyle{res}=[rectangle, rounded corners, minimum width = 2cm, minimum height = 1cm, text centered, draw = black, fill = blue!30]
\tikzstyle{resvariables}=[rectangle, minimum width = 2cm, minimum height = 1cm, text centered, draw = black]
\tikzstyle{steps} = [rectangle, minimum width = 1cm, text centered, fill = yellow]

%arrows
\tikzstyle{arrow} = [->, > = stealth, draw = black, color = yellow!80, line width = 6pt]

\begin{landscape}
%\parindent=0pt % extra spaces towards the edges
%\eject\null
%\vfill
%\hspace*{-4cm}

\begin{tikzpicture}[
  grow via three points={one child at (0.5,-1) and
  two children at (0.5,-1) and (0.5,-1.7)},
  edge from parent path={(\tikzparentnode.south) |- (\tikzchildnode.west)},
  remember picture, overlay, % r.p. save picture size in the picture, o. puts picture out of text segm.
  inner sep = 0pt, outer sep = 0pt
]

%%% nodes %%%
%% input
% TODO coordinates (-3,4) is strange. Also rectangle around current page seems wrong
\node[text=red] (io) [io, align = left] at (-3cm,4cm) {Table of Chemicals \\ CAS, Compound name}; % coordinates: (current page.east)

% \draw[thick] (current page.south west) rectangle (current page.north east); % debuging

%% chemicals
% id nodes
\node (cas) [ids, below of=io, yshift = -4cm] {CAS};
% main nodes
\node (chemprop) [main, dashed, right of=cas, xshift=4.5cm, yshift=3cm] {CHEMPROP};
\node (epa) [main, right of=cas, yshift=1cm, xshift=4.5cm] {EPA ectox tests}
	child { node { qu\_epa.R} };
\node (chemscr) [main, right of=cas, yshift=-1cm, xshift=4.5cm] {Chemical scripts ch}
	child { node { Alan Wood Pesticide Compendium - \textbf{qu\_aw.R } }}
	child { node { Pesticide Action Network - \textbf{ch\_pan.R} }}
	child { node { PhysProp - \textbf{ch\_pp.R} }}
	child { node { PubChem - \textbf{qu\_pubchem.R} }};
% result nodes
\node (toxres) [resvariables, right of=cas, yshift=0cm, xshift=16cm, align = left] {Results\\Test results\\Substance type:\\pesticides, metals, etc.}; % result
%\includegraphics{/home/andreas/Documents/Projects/etox-base/data/pubchemlogo2017.png};

%\animategraphics{https://cfpub.epa.gov/ecotox/epafiles/images/logo_epaseal.gif}

%% organisms
% id nodes
\node (taxon) [ids, below of=cas, yshift=-9cm, align = center] {Taxon}; % \\ {(Genus or Species)}}; % escape brackets usin curly brackets
% main nodes
\node (taxonquery) [main, right of=taxon, xshift=4.5cm, yshift=3cm] {Taxonomic data};
\node (habitat) [main, right of=taxon, xshift=4.5cm, yshift=1cm] {Habitat data}
	child { node { WORMS data base - \textbf{tx\_worms.R} }}
	child { node { Manual Search - \textbf{ha\_manual.R} }};
\node (region) [main, right of = taxon, xshift=4.5cm, yshift=-2cm] {Regional data}
	child { node { GBIF - \textbf{qu\_gbif.R} }};
% result nodes
\node (taxres) [resvariables, right of=taxon, xshift=17cm, align = left] {Results:\\Validation of taxonomic ranks\\Habitat information\\Marine, Bracksih, Freshwater, Terrestrial, Parasites\\Occurrence}; % result

%% final result
\node (testres) [res] at (18,-5) {Final result}
	child { node { re\_merge.R} };
\iffalse
node[anchor = south]
node[anchor = east]
\fi

%%% arrows %%%
\begin{pgfonlayer}{bg1}
\draw [arrow, black] (io) -- (cas);
\draw [arrow, dashed] (cas) -- (chemprop);
\draw [arrow] (cas) -- (chemscr);
\draw [arrow] (cas) -- (epa);
\draw [arrow] (epa) -- (toxres);
\draw [arrow] (chemscr) -- (toxres);

%\begin{scope}[on background layer]
\begin{pgfonlayer}{bg2}
	\draw [arrow, black] (epa) .. controls (-2,-4) and (1,-4) .. (taxon);
\end{pgfonlayer}
%\end{scope}

\draw [arrow] (taxon) -- (habitat);
\draw [arrow] (taxon) -- (region);
\draw [arrow] (taxon) -- (taxonquery);
\draw [arrow] (habitat) -- (taxres);
\draw [arrow] (taxonquery) -- (taxres);
\draw [arrow] (region) -- (taxres);
\draw [arrow] (toxres) -- (testres);
\draw [arrow] (taxres) -- (testres);

\draw [arrow] (testres) -- (22,-5);
\end{pgfonlayer}

\end{tikzpicture}
\end{landscape}

%\clearpage
%\thispagestyle{empty} % removes the 1

\begin{landscape}
\begin{tikzpicture}

@@

%% entities
\node (test) [res] at (-10,-10) {Test}; %debuging

\node (clean) [res] at (-5,5) {Cleaning}
	child { node { re\_clean.R} };
\node (filter) [res, right of = clean, xshift = 3cm] {Filter}
	child { node { re\_filter.R} };
\node (plot) [res, right of = filter, xshift = 3cm] {Plots}
	child { node { re\_plot.R} };
\node (agg1) [res, right of = plot, xshift = 3cm] {Aggregation};

\node (write) [io, right of = agg1, xshift = 3cm, yshift = -5cm] {Write tables to data base};

%% cleaning and filter steps
\node (solub) [steps, below of = clean, yshift = -2cm] {Solubility check};
\node (substtype) [steps, below of = solub, yshift = -2cm] {Substance-type: F, AI, U, T};

@@

%% boxes
\draw [dashed] (1,6) rectangle (3,-11);
\draw [dashed] (4,5) rectangle (7,-11);
\draw [dashed] (9,5) rectangle (11,-11);
\draw [dashed] (14,5) rectangle (15,-11);

\end{tikzpicture}
\end{landscape}

\end{document}

>>>>

\documentclass[border = 1.5cm]{standalone}
%%%% packages
\usepackage{tikz}
\usetikzlibrary{trees, arrows, shapes.geometric} % TikZ libraries
%%%% layers
\pgfdeclarelayer{bg1}    % declare background layer
\pgfdeclarelayer{bg2}
\pgfsetlayers{bg2,bg1,main}  % set the order of the layers (main is the standard layer)

%%%% styles
\tikzset{
	every rectangle node/.style = {draw=black,thick},
	io/.style = {rectangle, minimum width = 4cm, minimum height = 3cm, text centered, draw = black, fill = blue!10},
	main/.style = {rectangle, rounded corners, minimum width = 3cm, text centered, fill = purple!30},
	ids/.style = {diamond, minimum width = 3cm, minimum height = 2cm, text centered, draw = black, fill = green!30},
	res/.style = {rectangle, rounded corners, minimum width = 2cm, minimum height = 1cm, text centered, draw = black, fill = blue!30},
	resvariables/.style = {rectangle, minimum width = 2cm, minimum height = 1cm, text centered, draw = black},
	steps/.style = {rectangle, minimum width = 1cm, text centered, fill = yellow},
	txtfield/.style = {rectangle, rounded corners, text width = 3cm, minimum height = 6cm},
	arrow/.style = {->, > = stealth, draw = black, color = gray!80, shorten > = 2pt, line width = 3pt}
}

@@

	\begin{tikzpicture}[
	grow via three points={one child at (0.5,-1) and
		two children at (0.5,-1) and (0.5,-1.7)},
	edge from parent path={(\tikzparentnode.south) |- (\tikzchildnode.west)},
	anchor = west, inner sep = 0pt, outer sep = 0pt
	]

@@

	%% nodes	
	\node (clean) [res] at (0cm,0cm) {Cleaning}
	child { node { re\_clean.R} };
	\node (filter) [res, right of = clean, xshift = 3cm] {Filter}
	child { node { re\_filter.R} };
	\node (plot) [res, right of = filter, xshift = 3cm] {Plots}
	child { node { re\_plot.R} };
	\node (agg) [res, right of = plot, xshift = 3cm] {Aggregation}
	child { node { re\_aggregation.R} };

	\node (write) [io, right of = agg, xshift = 4cm, yshift = -3cm] {Write tables to data base};

	%% text fields
	%\node (txtclean2) [txtfield, below of = clean, yshift = -4cm] {Test2};
	\node (txtclean2) [txtfield, below of = clean, yshift = -4cm] {Try};
	\node (txtclean2) [txtfield, below of = filter, yshift = -4cm] {Tryasdf};
	\node (txtclean2) [txtfield, below of = plot, yshift = -4cm] {Tryasdf};
	\node (txtclean2) [txtfield, below of = agg, yshift = -4cm] {Tryasdf};

	%% arrows
	\draw [arrow] (clean) -- (filter);
	\draw [arrow] (filter) -- (plot);
	\draw [arrow] (plot) -- (agg);
	\draw [arrow, to path={-| (\tikztotarget)}] (agg) edge (write.north);

	%% cleaning and filter steps

	\iffalse
	\node (solub) [steps, below of = clean, yshift = -2cm] {Solubility check};
	\node (substtype) [steps, below of = clean, yshift = -4cm] {Substance-type: F, AI, U, T};

@@

	%% boxes
	\draw [dashed] (1,6) rectangle (3,-11);
	\draw [dashed] (4,5) rectangle (7,-11);
	\draw [dashed] (9,5) rectangle (11,-11);
	\draw [dashed] (14,5) rectangle (15,-11);
	\fi
	\end{tikzpicture}
\end{document}
